Language-Based Security for Low-Level MPC

### 2024-05-22 ppdp24/bruteforce.tex
checkpoint

In Figure \ref{fig-solve} we define the algorithm
$\solve{\stores}{\be}{\cid}$ which filters a given $\stores$ to obtain the
subset whose elements satisfy $\be$. In this figure and elsewhere for
$\mathbb{F}_2$ we use standard names of logical connectives
for field operations ($\eand$ and $\exor$ for $*$ and $+$ respectively) and
add $\enot$ and $\eor$ as trivial but convenient extensions. The correctness
of this operation is characterized as follows.
\begin{lemma}
  \label{lemma-solves}
  %For all $\stores$ and $\be$ with $\vars(\be) \subseteq \dom(\stores)$,
  $(\solve{\stores}{\be}{\cid}) = \{ \store \in \stores \ \mid\ \lcod{\store,\be}{\cid} = 1 \}$.
\end{lemma}

@@

  \vars\ (\be_1 \exor \be_2)\ \cid \defeq (\vars\ \be_1\ \cid) \cup (\vars\ \be_2\ \cid)
\end{mathpar}
... and so on. Then, to begin converting a protocol $\prot$ to a Datalog
we define the function ${tt}$ that applies $\solve{\!}{\!}{\!\!}$ locally to each command
in $\prog$, obtaining the subset of memories that result
in a variable assignment of $1$.  
\begin{definition} Define:
$$
\bodies(\xassign{x}{\be}{\cid}) \defeq (x, (\solve{(\mems(\vars\ \be\ \cid))}{\be}{\cid}))
$$
\end{definition}
The mapping of $\bodies$ across a program
$\prog$-- i.e., $(\mathit{map}\ \bodies\ \prog)$--  essentially defines the
logic program, modulo some syntactic conversion. We can
accomplish the latter as follows, where $\datalog(\prog)$ defines the
full conversion.
\begin{definition} We define the conversion from memories to
  literals and clause bodies as follows:
\begin{mathpar}
  \logit{x \mapsto 1} \defeq x

>>>>

In Figure \ref{fig-solve} we define the algorithm
$\solve{\stores}{\be}{\cid}$ which filters a given $\stores$ to obtain
the subset whose elements satisfy $\be$. In this Figure and elsewhere
we use logical connectives as field operations ($\eand$ and $\exor$
for $*$ and $+$ respectively) in $\mathbb{F}_2$ and add $\enot$ and
$\eor$ as trivial but convenient extensions. The correctness of this
operation is characterized as follows.
\begin{lemma}
  \label{lemma-solves}
  %For all $\stores$ and $\be$ with $\vars(\be) \subseteq \dom(\stores)$,
  $(\solve{\stores}{\be}{\cid}) = \{ \store \in \stores \ \mid\ \lcod{\store,\be}{\cid} = 1 \}$.
\end{lemma}

@@

  \vars\ (\be_1 \exor \be_2)\ \cid \defeq (\vars\ \be_1\ \cid) \cup (\vars\ \be_2\ \cid)
\end{mathpar}
... and so on. Then, to convert a protocol $\prot$ to a Datalog
we first define the function $\bodies$ that applies $\solvealg$ locally to each command
in $\prog$, obtaining the subset of memories that result
in a variable assignment of $1$.  
\begin{definition} Define:
$$
\bodies(\xassign{x}{\be}{\cid}) \defeq (x, (\solve{(\mems(\vars\ \be\ \cid))}{\be}{\cid}))
$$
\end{definition}
The mapping of $\bodies$ across a program
$\prog$-- i.e., $(\mathit{map}\ \bodies\ \prog)$--  essentially defines the
logic program, modulo some syntactic conversion. We can
accomplish the latter as follows, where $\datalog(\prog)$ defines the
full conversion.
\begin{definition} We define the conversion from memories to
  literals and clause bodies as follows:
\begin{mathpar}
  \logit{x \mapsto 1} \defeq x

### 2024-05-22 ppdp24/example-gmw.tex
checkpoint

As an extended example of our language and security model, and how the
automated techniques in Section \ref{section-bruteforce} can serve
as tactics integrated with PSL/Lilac-style proofs, we consider GMW
circuits.  The GMW protocol is a garbled binary circuit protocol.  We
will assume the 2-party version, though it generalizes to $n$
parties\cite{goldreich2019play}. GMW uses a common technique in MPC, which is to
represent values $v$ as distributed shares $v_1$ and $v_2$ with $v =
v_1 \fplus v_2$. This trick maintains secrecy of $v$ from both
parties, and in GMW it is used to maintain the intermediate values of
internal gate outputs in circuits. In related literature the notation
$\macgv{x}$ is used to represent the ``true'' value of $x$ and $[x]$
is often used to represent the share of given party.

@@

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, and includes encoding functions, where
input secrets are split into shares, $\eand$ and $\exor$ gate
functions, and a decoding function. Note that $\exor$ requires
no interaction between parties, while $\eand$ necessitates and
1-of-4 oblivious transfer. The gate computation is
done entirely in secrect, and the decoding function
is where the declassification occurs-- both parties reveal
their shares of the final gate output $\macgv{z}$.

@@

As discussed above and in related work \cite{8429300}, probabilistic
separation conditional on certain variables-- e.g., secret inputs or
public outputs-- is a key mechanism for reasoning about MPC protocol
security. Following \cite{barthe2019probabilistic}, we define a conditional separation
relation $\condsep{\pmf}{X_1}{X_2}{X_3}$ to mean that under the
condition of all value assignments for $X_2$ and $X_3$ are separable
under $\pmf$ on the condition of any value assignment of $X_1$-- i.e.,
conditionally on any $\store \in \mems(X_1)$. Another key concept
needed especially for reasoning about circuits is conditional
determinism. For example, if $\macgv{z}$ is an output of an internal
gate, it will definitely be computed using random variables, however,
it \emph{should} be determistic under any set of input secrets $S$,
since we assume that $\idealf$ is deterministic. Conditional
uniformity is also important, since the gradual release property of
many protocols means that messages appear in a uniform distribution to
the adversary.
\begin{definition}[Conditioning Properties] 
  Give $\pmf$ and $X_1,X_1,X_3 \subseteq \dom{pmf}$, 
  we write:
  \begin{itemize}
  \item $\condsep{\pmf}{X_1}{X_2}{X_3}$ iff for all
    $\store' \in \mems(X_1)$ and $\store \in \mems(X_2 \cup X_3)$ we have
    $\pmf(\store|\store') = \pmf(\store_{X_2}|\store') *  \pmf(\store_{X_3}|\store')$.
  \item $\conddetx{\pmf}{X_1}{X_2}$ iff for all
    $\store' \in \mems(X_1)$ there exists 
    $\store \in \mems(X_2)$ such that $\pmf(\store|\store') = 1$.
  \item $\condunix{\pmf}{X_1}{X_2}$ iff for all
    $\store' \in \mems(X_1)$ and
    $\store \in \mems(X_2)$ we have
    $\pmf(\store|\store') = 1/p^{|X_2|}$.
  \end{itemize}
\end{definition}

>>>>

As an extended example of our language and security model, and how the
automated techniques in Section \ref{section-bruteforce} can serve
as tactics integrated with PSL/Lilac-style proofs, we consider GMW
circuits.  The GMW protocol is a garbled binary circuit protocol.  We
will assume the 2-party version, though it generalizes to $n$
parties \cite{goldreich2019play}. GMW uses a common technique in MPC, which is to
represent values $v$ as distributed shares $v_1$ and $v_2$ with $v =
v_1 \fplus v_2$. This trick maintains secrecy of $v$ from both
parties, and in GMW it is used to maintain the intermediate values of
internal gate outputs in circuits. In related literature the notation
$\macgv{x}$ is used to represent the ``true'' value of $x$ and $[x]$
is often used to represent the share of given party.

@@

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, and includes encoding functions, where
input secrets are split into shares, $\eand$ and $\exor$ gate
functions, and a decoding function. Note that $\exor$ requires
no interaction between parties, while conjunction necessitates
1-of-4 oblivious transfer. The gate computation is
done entirely in secrect, and the decoding function
is where the declassification occurs-- both parties reveal
their shares of the final gate output $\macgv{z}$.

@@

As discussed above and in related work \cite{8429300}, probabilistic
separation conditional on certain variables-- e.g., secret inputs or
public outputs-- is a key mechanism for reasoning about MPC protocol
security. Following \cite{barthe2019probabilistic}, we define a
conditional separation relation $\condsep{\pmf}{X_1}{X_2}{X_3}$ to
mean that $X_2$ and $X_3$ are indpendent in $\pmf$ conditionally on
any assignment of values to $X_1$-- i.e., conditionally on any $\store
\in \mems(X_1)$. Another key concept needed especially for reasoning
about circuits is conditional determinism. For example, if $\macgv{z}$
is an output of an internal gate, it will definitely be computed using
random variables, however, it \emph{should} be determistic under any
set of input secrets $S$, since we assume that $\idealf$ is
deterministic. Conditional uniformity is also important, since the
gradual release property of many protocols means that messages appear
in a uniform distribution to the adversary.
\begin{definition}[Conditioning Properties] 
  Give $\pmf$ and $X_1,X_1,X_3 \subseteq \dom{pmf}$, 
  we write:
  \begin{itemize}
  \item $\condsep{\pmf}{X_1}{X_2}{X_3}$ iff for all
    $\store' \in \mems(X_1)$ and $\store \in \mems(X_2 \cup X_3)$ we have
    $\pmf(\store|\store') = \pmf(\store_{X_2}|\store') *  \pmf(\store_{X_3}|\store')$.
  \item $\conddetx{\pmf}{X_1}{X_2}$ iff for all
    $\store' \in \mems(X_1)$ there exists 
    $\store \in \mems(X_2)$ such that $\pmf(\store|\store') = 1$.
  \item $\condunix{\pmf}{X_1}{X_2}$ iff for all
    $\store' \in \mems(X_1)$ and
    $\store \in \mems(X_2)$ we have
    $\pmf(\store|\store') = 1/p^{|X_2|}$.
  \end{itemize}
\end{definition}
